Understanding the Lomb-Scargle Periodogram

### 2017-03-28 PracticalLombScargle.tex
Final tweaks for arXiv submission
fix some typos

\documentclass[preprint]{aastex}
%\documentclass{emulateapj}

@@

\usepackage{color}
\usepackage{url}
\usepackage{graphicx}
\usepackage{fancyhdr}
\graphicspath{{figures/}}

@@

\title{Understanding the Lomb-Scargle Periodogram\\
       {\it (Draft Version \today)}}

% Add ``Draft version'' footer
\pagestyle{fancy}
\fancyhf{}\renewcommand{\headrulewidth}{0pt} % remove header titles
\cfoot{\it \footnotesize $\sim$ Draft Version, \today $\ \sim$}

@@

The Lomb-Scargle periodogram computed from this data is shown in the left
panel  of \fig{LINEAR-data}.
The Lomb-Scargle periodogram here yields an estimate of the Fourier
power as a function of period of oscillation (\fig{LINEAR-power}, left), from
which we can read-off the period of oscillation of approximately 2.58 hours.
The right panel of \fig{LINEAR-power} shows a folded visualization of
the same data as \fig{LINEAR-data} -- i.e.{} plotted as a function of phase
rather than time.

>>>>

\documentclass[preprint]{aastex}
%\documentclass{emulateapj}
\pdfoutput=1

@@

\usepackage{color}
\usepackage{url}
\usepackage{graphicx}
\usepackage{fancyhdr}
\graphicspath{{./}{figures/}}

@@

\title{Understanding the Lomb-Scargle Periodogram}

%\title{Understanding the Lomb-Scargle Periodogram\\
%       {\it (Draft Version \today)}}

% Add ``Draft version'' footer
%\pagestyle{fancy}
%\fancyhf{}\renewcommand{\headrulewidth}{0pt} % remove header titles
%\cfoot{\it \footnotesize $\sim$ Draft Version, \today $\ \sim$}

@@

The Lomb-Scargle periodogram computed from this data is shown in the left
panel  of \fig{LINEAR-power}.
The Lomb-Scargle periodogram here yields an estimate of the Fourier
power as a function of period of oscillation, from
which we can read-off the period of oscillation of approximately 2.58 hours.
The right panel of \fig{LINEAR-power} shows a folded visualization of
the same data as \fig{LINEAR-data} -- i.e.{} plotted as a function of phase
rather than time.
